The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-15 paper/ms.tex
lomb-scargle

\begin{figure*}
\plotone{rho_leo_pub.pdf}
\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for $\rho$~Leonis. The top three panels illustrate \textsc{k2sc} systematics correction: at the top, flux minus the GP time trend (blue dots) with GP $x,y$ trend superimposed (orange line); in the middle, flux minus GP $x,y$ components with GP time trend superimposed, and in green, a fifteenth-order polynomial trend; at the bottom the `whitened' light curve with flux minus both GP components. Middle two panels: log-flux map (left) and halo log-weight map (right). Bottom two panels: Lomb-Scargle power spectra in linear (top) and log (bottom) scales of the residuals of the corrected light curve minus the long term polynomial trend. Plots of this form are available in supplementary online material for all long-cadence stars, together with similar plots for all short-cadence stars but without \textsc{k2sc}. The period at maximum power (16\,d) is marked on all plots of this form; in $\rho$~Leo, variability is attributed to red noise and a 26.8~d rotation period \citep{Aerts2018,bowman19}.}
\label{fig:rholeo}
\end{figure*}

>>>>

\begin{figure*}
\plotone{rho_leo_pub.pdf}
\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for $\rho$~Leonis. The top three panels illustrate \textsc{k2sc} systematics correction: at the top, flux minus the GP time trend (blue dots) with GP $x,y$ trend superimposed (orange line); in the middle, flux minus GP $x,y$ components with GP time trend superimposed, and in green, a fifteenth-order polynomial trend; at the bottom the `whitened' light curve with flux minus both GP components. Middle two panels: log-flux map (left) and halo log-weight map (right). Bottom two panels: Lomb-Scargle power spectra \citep{lomb,scargle} in linear (top) and log (bottom) scales of the residuals of the corrected light curve minus the long term polynomial trend. Plots of this form are available in supplementary online material for all long-cadence stars, together with similar plots for all short-cadence stars but without \textsc{k2sc}. The period at maximum power (16\,d) is marked on all plots of this form; in $\rho$~Leo, variability is attributed to red noise and a 26.8~d rotation period \citep{Aerts2018,bowman19}.}
\label{fig:rholeo}
\end{figure*}
